The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-01 registry.tex
Using latest version of the package registry to generate the table

\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS} \\

@@

>>>>

\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan} \\

@@

\href{https://github.com/spacetelescope/spherical_geometry.git}{spherical\_geometry} & No & \href{https://pypi.python.org/pypi/spherical-geometry}{spherical-geometry} & Bernie Simon and Michael Droettboom &  \\
